---
title: "Assignment - BIG DATA ANALYTICS"
author: "Dominik Walter & Greta Kurpicz"
date: "22 4 2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readtext)
library(quanteda)
library(quanteda.textmodels)
library(cowplot)
library(quanteda.textplots)
library(PerformanceAnalytics)
library(psych)
library(tidyverse)

```

Information: Due to difficulties on both ends, we decided to do all exercise together. We met several times on zoom and discussed all approaches. Therefore the output below is equally from the both of us.  

# Part 1

## Preparation
### Loading data
```{r}
myText <- readtext("UK new manifestoes/*.txt", 
                   docvarsfrom = "filenames", dvsep = " ", docvarnames = c("Party", "Year"))
myText <- gsub("[\u00E2]","",myText$text) 


testCorpus <- corpus(myText )
docnames(testCorpus) <- gsub(".txt", "", docnames(testCorpus ))
```

### Creating DfM

```{r}
myDfm <- dfm(testCorpus , remove = stopwords("smart"), tolower = TRUE, stem = TRUE,
             remove_punct = TRUE, remove_numbers=TRUE, split_hyphens = TRUE)
topfeatures(myDfm , 20)  # 20 top words
myDfm <- dfm_remove(myDfm, min_nchar=2)
```


## Wordfish
```{r}
# here: Lab 2010 to the left of UKIP 2015 to the right
wfm <- textmodel_wordfish(myDfm, dir = c(4, 11))
summary(wfm)
textplot_scale1d(wfm, margin = "documents")

```

## Wordscores
```{r}
# keep only words occurring >1 times
myDfm <- dfm_trim(myDfm, min_termfreq = 2)

# compute some document similarities
Simil <- textstat_simil(myDfm , method = "correlation")
Simil

```


### Set reference score

```{r}
ref_eco <- c(NA, 7.85, NA, NA, 3.85, NA, NA, 5.14, NA, NA, 8.57, NA)
ref_eu <- c(NA,3.14,NA,NA,5.57,NA,NA,6.71,NA,NA,1.14,NA)
```


### Ref score to Dfm
```{r}
ws_eco <- textmodel_wordscores(myDfm, ref_eco)
ws_eu <- textmodel_wordscores(myDfm, ref_eu)
summary(ws_eco)
summary(ws_eu) 
```


### Predict raw Wordscores for all the texts (reference and virgin ones)
```{r}
pr_eco <- predict(ws_economy, rescaling = "lbg", newdata = myDfm[c(1,3,4,6,7,9,10,12), ])
pr_eu <- predict(ws_eu, rescaling = "lbg", newdata = myDfm[c(1,3,4,6,7,9,10,12), ])

pr_economy
pr_eu



# add the prediction scores to the reference scores --> DO ISCH MIS PROBLEM VILICHT WEISCH DU MEH@ GRETA
scores_economy <- c(5.690635, 5.825176, 4.927647, 4.506773, 5.195472, 4.940397, 9.907417, 9.905901)
scores_eu <- c(4.80248034, 4.76073830, 5.47054701, 5.52623858, 5.77116977, 6.43145194, 0.37347041, 0.02879203 )


# assign it to the texts
ws_economy <- textmodel_wordscores(myDfm,scores_economy)
ws_eu <-textmodel_wordscores(myDfm,scores_eu)
```



